Exploring Hillary Clinton's Emails\thanks{STATS 601 final project.}

### 2016-04-18 paper/paper.tex
Working on figures/tables.

% General
\usepackage[round]{natbib}
\usepackage{setspace}
\usepackage{geometry}
\usepackage[section]{placeins}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}
\usepackage{color}
\usepackage{titlesec}
\usepackage[page]{appendix}
\usepackage{enumerate}

@@

@@

@@

@@

>>>>

% General
\usepackage[round]{natbib}
\usepackage{setspace}
\usepackage{geometry}
\usepackage[section]{placeins}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage[page]{appendix}
\usepackage{enumerate}

@@

\usepackage{tikz}

@@

\newcommand*{\colsquare}[3][-3.5pt]{\tikz[baseline=-0.5ex]\draw[#2, fill=#2] (0,#1) rectangle ++(#3,#3);}%
\definecolor{cmeet}{HTML}{E31A1C}
\definecolor{cmideast}{HTML}{1F78B4}
\definecolor{cstaff}{HTML}{A6CEE3}
\definecolor{cpolitics}{HTML}{33A02C}
\definecolor{cterror}{HTML}{B2DF8A}
\definecolor{cforeign}{HTML}{FB9A99}
\definecolor{cpress}{HTML}{FF7F00}
\definecolor{chill}{HTML}{6A3D9A}
\definecolor{ccommu}{HTML}{CAB2D6}
\definecolor{ccomm}{HTML}{FDBF6F}

@@

We define the cosine similarity between word frequency vectors $V$ and $W$ to be the cosine of the angle between the two vectors, calculated as
\begin{equation} \label{eq:cos_sim}
\cos(\phi) = \frac{\langle V, W \rangle}{\norm{V}\norm{W}}
\end{equation}
Since counts must be nonnegative, note that $\phi \leq \pi/2$. This implies that the cosine similarity is always between 0 and 1, with 0 corresponding to parallel vectors and 1 corresponding to orthogonal vectors. So we can define the cosine distance as
\begin{equation} \label{eq:cos_dist}
d(V, W) = 1 - \cos(\phi) = 1 - \frac{\langle V, W \rangle}{\norm{V}\norm{W}}
\end{equation}

\begin{figure}[htb] \centering
  \begin{subfigure}[t]{.49\linewidth}
    \includegraphics[width=\linewidth]{../images/mds_2d.png}
    \caption{2 Dimensions} \label{fig:mds:2d}
  \end{subfigure}
  \begin{subfigure}[t]{.49\linewidth}
    \includegraphics[width=\linewidth]{../images/mds_3d_1.png}
    \caption{3 Dimensions} \label{fig:mds:3d}
  \end{subfigure}
  \caption{Visualization of a 8,000 email subset using classical multi-dimensional scaling. The distance metric used is cosine distance as defined in Equation~\ref{eq:cos_dist}.}
  \label{fig:mds}
\end{figure}

\begin{figure}[htbp] \centering
  \begin{subfigure}[t]{.7\linewidth}
    \includegraphics[width=\linewidth]{../images/mds_2d_cluster.png}
    \caption{2 Dimensions} \label{fig:cluster:2d}
  \end{subfigure}
  \begin{subfigure}[t]{.7\linewidth}
    \includegraphics[width=\linewidth]{../images/mds_3d_cluster_1.png}
    \caption{3 Dimensions} \label{fig:cluster:3d}
  \end{subfigure}
  \caption{Visualization of the same 8,000 email subset with coloring according to the results from spectral clustering.}
  \label{fig:cluster}
\end{figure}

@@

\begin{table}[htb] \centering
\begin{tabular}{rcl}
  \toprule
  \colsquare{cterror}{10pt} & Terrorism & 5, 22 \\
  \colsquare{cmideast}{10pt} & Middle East & 6, 18, 19, 27, 29 \\
  \colsquare{cforeign}{10pt} & Foreign Policy & 2, 7, 13, 21, 23, 26 \\
  \colsquare{cpolitics}{10pt} & Politics & 11, 17, 25 \\
  \colsquare{cstaff}{10pt} & Staff & 16, 20 \\
  \colsquare{cpress}{10pt} & Press & 4 \\
  \colsquare{chill}{10pt} & Hillary & 12 \\
  \colsquare{cmeet}{10pt} & Meetings & 9, 10, 24, 28, 30 \\
  \colsquare{ccommu}{10pt} & Communication & 1 \\
  \colsquare{ccomm}{10pt} & Common & 3, 8, 14, 15 \\
  \bottomrule
\end{tabular}
\caption{Topic Categorization}
\label{tab:topic_cat}
\end{table}

\begin{table}[htb] \centering
\setlength{\tabcolsep}{1pt}
\begin{tabular}{ccccccccccccccccccccccccc}
  \toprule
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cmeet}{16pt} &
  \colsquare[-3pt]{cmeet}{16pt} &
  \colsquare[-3pt]{cmeet}{16pt} &
  \colsquare[-3pt]{cmeet}{16pt} &
  \colsquare[-3pt]{cpress}{16pt} &
  \colsquare[-3pt]{cmeet}{16pt} &
  \colsquare[-3pt]{cmideast}{16pt} &
  \colsquare[-3pt]{cmideast}{16pt} &
  \colsquare[-3pt]{cstaff}{16pt} &
  \colsquare[-3pt]{cstaff}{16pt} &
  \colsquare[-3pt]{chill}{16pt} &
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cpolitics}{16pt} &
  \colsquare[-3pt]{cmideast}{16pt} &
  \colsquare[-3pt]{cmideast}{16pt} &
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cmideast}{16pt} &
  \colsquare[-3pt]{cterror}{16pt} &
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cpolitics}{16pt} &
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cpolitics}{16pt} &
  \colsquare[-3pt]{cterror}{16pt} \\
  21 & 28 & 30 & 9 & 10 & 4 & 24 & 29 & 18 & 20 & 16 & 12 &
  13 & 17 & 19 & 27 & 23 & 6 & 22 & 2 & 25 & 26 & 7 & 11 & 5 \\
  \bottomrule
\end{tabular}
\setlength{\tabcolsep}{6pt}
\caption{Primary Topic Frequency}
\label{tab:topic_freq}
\end{table}
